Stellar Migration and Chemical Enrichment in the Milky Way Disc: A Hybrid Model

### 2021-08-04 chemev/MWbimodality/paper/draft3/conclusions.tex
migration paper referee response

% fig 17 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
late-burst (bottom) SFH models for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
the corresponding Galactic region, but with the model prediction quantified in 
bins of~$\Delta$[Fe/H] = 0.05. } 
\label{fig:amr_insideout_vs_lateburst_fe} 
\end{figure*}

In this paper, we have modeled the Milky Way as a series of concentric rings 
with~$\Delta R_\text{gal}$~= 100 pc width, describing each ring as a 
conventional one-zone chemical evolution model and allowing the exchange of 
stellar populations between zones to include the impact of stellar migration in 
the model Galaxy. 
Though there have been other studies that employ a similar methodology 
\citep[e.g.][]{Schoenrich2009a, Schoenrich2009b, Kubryk2015a, Kubryk2015b, 
Sharma2020}, ours and the~\citet{Minchev2013, Minchev2014, Minchev2017} model 
are the only ones that make use of a hydrodynamical simulation to describe 
radial mixing. 
In our case we use the~\hsim~zoom-in simulation of a Milky Way-like disc galaxy 
formed from cosmological initial conditions~\citep{Christensen2012, 
Zolotov2012, Loebman2012, Brooks2014, Bird2020}. 
The simulation provides a prescription for radial migration and vertical 
structure with no free parameters, though there is still a choice to be made 
about how to model the time dependence of migration for a given stellar 
population (see~\S~\ref{sec:methods:migration}). 
In our fiducial prescription, a stellar population traverses the~$\Delta\rgal$ 
between its birth and final radius with a~$\sqrt{t}$ time-dependence 
characteristic of diffusion, as in~\citet{Frankel2018, Frankel2020}. 
While CCSN nucleosynthetic products are deposited instantaneously in the 
population's birth annulus, its SN Ia iron production follows a~$t^{-1.1}$ 
delay-time distribution and is therefore spread across all the annuli that it 
traverses. 
\par 
We adopt supernova yields from oxygen and iron based on a combination of 
theoretical and empirical constraints. 
We base our star formation law on the observed 
$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation in local spirals 
\citep{Bigiel2010, Leroy2013, Krumholz2018a}, with the redshift dependence 
suggested by the observations of~\citet{Tacconi2018}. 
We choose a radially dependent outflow mass loading factor~$\eta(\rgal)$ to 
reproduce observations of the Galactic disc metallicity 
gradient~\citep[e.g.][]{Frinchaboy2013, Hayden2014, Weinberg2019}. 
Our fiducial model adopts an inside-out SFH with e-folding timescales 
calibrated to the~\citet{Sanchez2020} age gradients of low redshift disc 
galaxies (see discussion in~\S~\ref{sec:methods:sfhs}). 
Motivated by the observational results of~\citet{Mor2019} and~\citet{Isern2019}, 
we construct models that exhibit a recent burst in star formation on top of the 
baseline model, as well as a constant SFH model for comparison purposes. 
\par 
We have compared our fiducial inside-out SFH model and its variants to a 
variety of observations, most of them derived from the SDSS APOGEE survey 
\citep{Majewski2017}, finding a number of qualitative successes but also some 
significant qualitative discrepancies. 
\begin{enumerate}

@@

	\item[\textbf{6.}] While most stars with~\ofe~$\geq$ 0.1 are old, the model 
	predicts a population of young and intermediate-age $\alpha$-rich stars. 
	These stars form in the outer Galaxy (\rgal~> 10 kpc) at times when the SN 
	Ia rate, and thus the iron enrichment, has fluctuated to low values because 
	stellar populations have migrated away before most of their SN Ia have time 
	to explode (see Fig.~\ref{fig:tracks}). 
	This mechanism, which is only realized because we track SN Ia enrichment 
	through rings as populations migrate (\S~\ref{sec:methods:migration}), 
	offers a novel explanation for the existence of young and intermediate-age 
	$\alpha$-rich stars seen in APOGEE~\citep{Chiappini2015, Martig2015, 
	Martig2016, Warfield2021}. 
	See Figs.~\ref{fig:age_alpha} and~\ref{fig:age_alpha_regions}.

@@

simulations that give rise to bimodal~\afe~\citep{Mackereth2017, Grand2018, 

@@

cosmological simulations~\citep[e.g.][]{Mackereth2017, Grand2018, Naiman2018, 

>>>>

In this paper, we have modeled the Milky Way as a series of concentric rings 
with~$\delta R_\text{gal}$~= 100 pc width, describing each ring as a 
conventional one-zone chemical evolution model and allowing the exchange of 
stellar populations between zones to include the impact of stellar migration in 
the model Galaxy. 
Though there have been other studies that employ a similar methodology 
\citep[e.g.][]{Schoenrich2009a, Schoenrich2009b, Kubryk2015a, Kubryk2015b, 
Sharma2020}, ours and the~\citet{Minchev2013, Minchev2014, Minchev2017} model 
are the only ones that make use of a hydrodynamical simulation to describe 
radial mixing. 
In our case we use the~\hsim~zoom-in simulation of a Milky Way-like disc galaxy 
formed from cosmological initial conditions~\citep{Christensen2012, 
Zolotov2012, Loebman2012, Brooks2014, Bird2021}. 
The simulation provides a prescription for radial migration and vertical 
structure with no free parameters, though there is still a choice to be made 
about how to model the time dependence of migration for a given stellar 
population (see~\S~\ref{sec:methods:migration}). 
In our fiducial prescription, a stellar population traverses the~$\Delta\rgal$ 
between its birth and final radius with a~$\sqrt{t}$ time-dependence 
characteristic of diffusion, as in~\citet{Frankel2018, Frankel2020}. 
While CCSN nucleosynthetic products are deposited instantaneously in the 
population's birth annulus, its SN Ia iron production follows a~$t^{-1.1}$ 
delay-time distribution and is therefore spread across all the annuli that it 
traverses. 
\par 
We adopt supernova yields from oxygen and iron based on a combination of 
theoretical and empirical constraints. 
We base our star formation law on the observed 
$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation in local spirals 
\citep{Bigiel2010, Leroy2013, Krumholz2018a}, with the redshift dependence 
suggested by the observations of~\citet{Tacconi2018}. 
We choose a radially dependent outflow mass loading factor~$\eta(\rgal)$ to 
reproduce observations of the Galactic disc metallicity 
gradient~\citep[e.g.][]{Frinchaboy2013, Hayden2014, Weinberg2019}. 
Our fiducial model adopts an inside-out SFH with e-folding timescales 
calibrated to the~\citet{Sanchez2020} age gradients of low redshift disc 
galaxies (see discussion in~\S~\ref{sec:methods:sfhs}). 
Motivated by the observational results of~\citet{Mor2019} and~\citet{Isern2019}, 
we construct models that exhibit a recent burst in star formation on top of the 
baseline model, as well as a constant SFH model for comparison purposes. 
\par 
We have compared our fiducial inside-out SFH model and its variants to a 
variety of observations, most of them derived from the SDSS APOGEE survey 
\citep{Majewski2017}, finding a number of qualitative successes but also some 
significant qualitative discrepancies. 
\begin{enumerate}

@@

	\item[\textbf{6.}] While most stars with~\ofe~$\geq$ 0.1 are old, the model 
	predicts a population of young and intermediate-age $\alpha$-rich stars. 
	These stars form in the outer Galaxy (\rgal~> 10 kpc) at times when the SN 
	Ia rate, and thus the iron enrichment, has fluctuated to low values because 
	stellar populations have migrated away before most of their SN Ia have time 
	to explode (see Fig.~\ref{fig:tracks}). 
	This mechanism, which is only realized because we track SN Ia enrichment 
	through rings as populations migrate (\S~\ref{sec:methods:migration}), 
	offers a novel explanation for the existence of young and intermediate-age 
	$\alpha$-rich stars seen in APOGEE~\citep{Chiappini2015, Martig2015, 
	Martig2016, Jofre2016, Yong2016, Izzard2018, SilvaAguirre2018, 
	Warfield2021}. 
	See Figs.~\ref{fig:age_alpha} and~\ref{fig:age_alpha_regions}.

@@

simulations that give rise to bimodal~\afe~\citep{Mackereth2018, Grand2018, 

@@

cosmological simulations~\citep[e.g.][]{Mackereth2018, Grand2018, Naiman2018, 

### 2021-08-04 chemev/MWbimodality/paper/draft3/intro.tex
migration paper referee response

@@

of the observed element structure (e.g., ~\citealt{Mackereth2017, Grand2018, 

@@

representative~$\alpha$-element producted almost exclusively by core 

@@

	``rejuvinated'' by stellar mergers or mass-transfer events 
	\citep{Izzard2018, SilvaAguirre2018}, and the question of what fraction 
	are truly much younger than the median age-\afe~relation remains open 
	\citep{Hekker2019}. 

@@

Most directly relevant to this study,~\citet{Bird2020} demonstrate that 

@@

The good match to the observed age-velocity relation found by~\citet{Bird2020} 

@@

have advocated a two-phase SFH to explain the~\afe dichotomy (e.g., 
\citealp*{Chiappini1997};~\citealp{Haywood2016, Spitoni2019a, Buck2020a, 
Khoperskov2021}). We do not investigate these more complex SFHs here, but we 
plan to do so in future work.

>>>>

\null\par 

@@

of the observed element structure (e.g.,~\citealt{Mackereth2018, Grand2018, 

@@

representative~$\alpha$-element produced almost exclusively by core 

@@

	``rejuvenated'' by stellar mergers or mass-transfer events 
	\citep{Jofre2016, Yong2016, Izzard2018, SilvaAguirre2018}, and 
	the question of what fraction are truly much younger than the median 
	age-\afe~relation remains open~\citep{Hekker2019, Miglio2021}. 

@@

Most directly relevant to this study,~\citet{Bird2021} demonstrate that 

@@

The good match to the observed age-velocity relation found by~\citet{Bird2021} 

@@

have advocated a two-phase SFH to explain the~\afe~dichotomy (e.g., 
\citealp*{Chiappini1997};~\citealp{Haywood2016, Mackereth2018, Spitoni2019a, 
Buck2020a, Khoperskov2021}). We do not investigate these more complex SFHs 
here, but we plan to do so in future work.
